2022-04-11 & 9AM-1PM & 4 & Debugging empty cells issue during SDCEL save, Catching bug during segment merging, Testing load method for individual SDCELs, Working on reports. \\ \hline
2022-04-12 & 9AM-1PM & 4 & Running new set of experiments, Debugging overlay alternative with MainUS dataset, Removing isBorder attribute from Segment and Half\_edge classes, Debugging segment generation during overlayMaster function. \\ \hline
2022-04-13 & 9AM-1PM & 4 & Fixing bug during overlayMaster and overlayByLevel, Setting holes correctly during overlay alternatives, Tracking performance with OR and CA datasets, Tuning performance script. \\ \hline
2022-04-14 & 9AM-1PM & 4 & Double checking performance issues, Tracking issue during mergeSegments in CA dataset, Plotting experiments from last results, Collecting results from OR and CA datasets. \\ \hline
2022-04-15 & 9AM-1PM & 4 & Completing Tax filing, Attending privacy location data seminar, Advancing training for staff assignment. \\ \hline
2022-04-18 & 9AM-1PM & 4 & Running experiments for overlay alternatives in 8 biggest states, Tuning plots and new experiments for overlay alternatives, Plotting new figures and descriptions on paper, Sync LaTeX versions of the paper. \\ \hline
2022-04-19 & 9AM-1PM & 4 & Running speed up test in GADM, Tuning template of the paper and sync with overleaf, Adding section for overlay methods evaluation, Running a set of new experiments with VA and PA datasets, Tuning plots for the new results. \\ \hline
2022-04-20 & 9AM-1PM & 4 & Advancing in training assigment, Working on generation of dataset splits for GADM scale up, Running speedup test for individual layers in MainUS, Collecting and plotting data from last experiment. \\ \hline
2022-04-21 & 9AM-1PM & 4 & Running cumulative sum over layer1 and layer2 of GADM dataset, Pruning empty cells in the perimeter for testing purposes, Uploading scale up datasets to HDFS and running the experiment, Moving data to server and spliting by 1/4 of number of total edges. \\ \hline
2022-04-22 & 9AM-1PM & 4 & Plotting results for MainUS speedup, Advancing on training assignment, Running scale up experiments for GADM, Fixing bug during the pruen of empty cells in the perimeter. \\ \hline
2022-04-25 & 9AM-1PM & 4 & Running with less data and iterations, Fix issue with GADM scaleup, Updating report, Sync with Overleaf, Collecting and plotting data for GADM scaleup experiment. \\ \hline
